### 2004-12-06 doc/Simulation_and_Control_using_Supremica/functionblocks.tex
*** empty log message ***

@@

\subsection{System Model} 
At the physical level, a distributed system consists of a
set of co-operating {\it applications}. An application can
exist on a single system such as application C in figure
\ref{f:System_Model} or have functionality distributed over
a number of devices such as applications A and B in Figure
\ref{f:System_Model}.

@@

\subsection{Device Model} 
A resource provides independent execution and control of
networks of function blocks. It supports zero or more {\it
  resources} and has at least one interface. The interface
could either be a 'process interface' that allows the
resources to exchange data with the input and output points
on the physical devices, or a communication interface that
allows the resources to communicate with external resources
in remote devices. The device model is illustrated in Figure
\ref{f:Device_Model}.

@@

\subsection{Resource Model} 
A resource is an independent functional unit, contained in a
device which has independent control of its operation. The
resource can be created, configured, parameterized, started
up, deleted etc. without effecting other resources. Each
resource provides an interface to the communication systems
and tot the device specific process. The resource is
therefore, concerned with the mapping of data and event
flows which pass between function blocks in the local
resource to remove resource function blocks via the device
communication interfaces.

@@

\subsection{Application Model} 
An application is defined as a network of interconnected
function blocks, linked by data and event flows. An
application can be fragmented and distributed over many
resources. The resources ensure that the events are executed
in the correct serial order based on the causal
relationships specified by the applications.

@@

\subsection{Function Block Model} 
A function block is a functional unit of software that its
own data structure which can be manipulated by one or more
algorithms. The formal description of the data structure is
provided by the function block type definition.

@@

\subsection{Basic Function Block Types} 
The behavior of basic function blocks is defined in terms of
algorithms that are invoked in response to input events. As
algorithms execute, they trigger output events to signal
their state to other blocks. The basic blocks hold their
state in terms of internal variables. Basic function blocks
also can communicate their state using input and output data
variables.

@@

\subsection{Composite Function Blocks} 
The behavior of a composite function block is described in
terms of the event and data connections between its
component function blocks. A composite function block can be
used to hide the internal interactions between the component
blocks and presenting a simplified interface for use by the
outside world. A composite function block is illustrated in
Figure \ref{f:Composite_Block}.

@@

\subsection{Service Interface Function Blocks} 
Service interface function blocks provide an interface
between the function block domain and the external services.
Since a service interface function block is primarily
concerned with data exchange, it is defined using time
sequence diagrams. Examples of service interface function
blocks are communication blocks for publishing and
subscribing over a network and management blocks for
dynamically creating component blocks and event connections.

\subsection{Event Function Blocks} 
Event function blocks are some special basic function blocks
defined in the standard to ease the management of events.
These blocks are used for control, generation and detection
of events and can be used by other composite blocks. These
blocks are defined using an execution control chart or a
time sequence diagram. These blocks can be used for the
following purposes:
\begin{enumerate}
\item To split events to produce new events.
\item To allow events to be merged.
\item To permit the propagation of certain events.
\item To select between two or more events.
\item To delay an event by a given period.
\item To generate a stream of events at a regular interval.
\end{enumerate}

>>>>

% -*- TeX-master:"main" -*-

@@

\subsection*{System Model} 
At the physical level, a distributed system consists of a
set of co-operating {\it applications}. An application can
exist on a single system such as application C in figure
\ref{f:System_Model} or have functionality distributed over
a number of devices such as applications A and B in Figure
\ref{f:System_Model}.

@@

\subsection*{Device Model} 
A resource provides independent execution and control of
networks of function blocks. It supports zero or more {\it
  resources} and has at least one interface. The interface
could either be a 'process interface' that allows the
resources to exchange data with the input and output points
on the physical devices, or a communication interface that
allows the resources to communicate with external resources
in remote devices. The device model is illustrated in Figure
\ref{f:Device_Model}.

@@

\subsection*{Resource Model} 
A resource is an independent functional unit, contained in a
device which has independent control of its operation. The
resource can be created, configured, parameterized, started
up, deleted etc. without effecting other resources. Each
resource provides an interface to the communication systems
and tot the device specific process. The resource is
therefore, concerned with the mapping of data and event
flows which pass between function blocks in the local
resource to remove resource function blocks via the device
communication interfaces.

@@

\subsection*{Application Model} 
An application is defined as a network of interconnected
function blocks, linked by data and event flows. An
application can be fragmented and distributed over many
resources. The resources ensure that the events are executed
in the correct serial order based on the causal
relationships specified by the applications.

@@

\subsection*{Function Block Model} 
A function block is a functional unit of software that its
own data structure which can be manipulated by one or more
algorithms. The formal description of the data structure is
provided by the function block type definition.

@@

\subsection*{Basic Function Blocks} 
The behavior of basic function blocks is defined in terms of
algorithms that are invoked in response to input events. As
algorithms execute, they trigger output events to signal
their state to other blocks. The basic blocks hold their
state in terms of internal variables. Basic function blocks
also can communicate their state using input and output data
variables.

@@

\subsection*{Composite Function Blocks} 
The behavior of a composite function block is described in
terms of the event and data connections between its
component function blocks. A composite function block can be
used to hide the internal interactions between the component
blocks and presenting a simplified interface for use by the
outside world. A composite function block is illustrated in
Figure \ref{f:Composite_Block}.

@@

\subsection*{Service Interface Function Blocks} 
Service interface function blocks provide an interface
between the function block domain and the external services.
Since a service interface function block is primarily
concerned with data exchange, it is defined using time
sequence diagrams. Examples of service interface function
blocks are communication blocks for publishing and
subscribing over a network and management blocks for
dynamically creating component blocks and event connections.

\subsection*{Event Function Blocks} 
Event function blocks are some special basic function blocks
defined in the standard to ease the management of events.
These blocks are used for control, generation and detection
of events and can be used by other composite blocks. These
blocks are defined using an execution control chart or a
time sequence diagram. These blocks can be used for the
following purposes:
\begin{enumerate}
\item To split events to produce new events.
\item To allow events to be merged.
\item To permit the propagation of certain events.
\item To select between two or more events.
\item To delay an event by a given period.
\item To generate a stream of events at a regular interval.
\end{enumerate}

### 2004-12-06 doc/Simulation_and_Control_using_Supremica/introduction.tex
*** empty log message ***

Define the problem.
Define other approaches, state of the art.
Introduce Function Blocks
Introduce Automation Objects
(Configuration, Simulation, Control, HMI)

>>>>

%Define the problem.
Ever increasing competition forces companies to diversify
their product lines. To achieve customizable products the
companies require constantly changing and evolving
production plants. Such plants are called flexible
production plants. The plant is constantly adopted to the
products with goal of producing the highest quality products
in as little time as posibble. To achieve this the software
for the automatic control of such a plant has to be changed
along with the plant. The problem is that using today
established development methods this is impossible without
stoping of the production.

%Define other approaches, state of the art.

%Introduce Function Blocks

%Introduce Automation Objects
